PineAPPL:\\ EW and mixed QCD--EW corrections for PDF fits

### 2020-07-30 paper/sec-results.tex
Typos

\paragraph{Top-quark pair production.}
We select the distributions, single-differential in either the transverse
momentum of the top quark, $p_T^t$, or the invariant mass of the top-quark
pair, $m_{t\bar t}$, measured by the ATLAS and CMS experiments at a centre-of-mass
energy of 8~TeV~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
been extensively studied in the context of PDF fits in
Refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml}, and
included by default in the CT18~\cite{Hou:2019efy} analysis.
Because EW corrections are significantly smaller for distributions differential
in the rapidity of either the top quark or the top-quark
pair~\cite{Czakon:2017wor}, these distributions were preferred for inclusion
in the NNPDF3.1 analysis~\cite{Ball:2017nwa}. The process receives 
pure QCD contributions at LO, $\mathcal{O}(\alpha_s^2)$, and
at NLO, $\mathcal{O}(\alpha_s^2)$. They are included in the NLO QCD
computation. The NLO QCD+EW computation includes the LO contribution
$\mathcal{O}(\alpha_s^1\alpha^1)$ and the NLO contributions
$\mathcal{O}(\alpha_s^2\alpha)$ and $\mathcal{O}(\alpha_s\alpha^2)$.
We do not consider the LO PI contribution $\mathcal{O}(\alpha^2)$ and the
corresponding higher-order EW correction. EW corrections for this process
were computed in Refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}. The process receives contributions from
6 (36) parton luminositites at NLO QCD (NLO QCD+EW), mainly from $gg$ fusion.

>>>>

\paragraph{Top-quark pair production.}
We select the distributions, single-differential in either the transverse
momentum of the top quark, $p_T^t$, or the invariant mass of the top-quark
pair, $m_{t\bar t}$, measured by the ATLAS and CMS experiments at a centre-of-mass
energy of 8~TeV~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
been extensively studied in the context of PDF fits in
Refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml}, and
included by default in the CT18~\cite{Hou:2019efy} analysis.
Because EW corrections are significantly smaller for distributions differential
in the rapidity of either the top quark or the top-quark
pair~\cite{Czakon:2017wor}, these distributions were preferred for inclusion
in the NNPDF3.1 analysis~\cite{Ball:2017nwa}. The process receives 
pure QCD contributions at LO, $\mathcal{O}(\alpha_s^2)$, and
at NLO, $\mathcal{O}(\alpha_s^3)$. They are included in the NLO QCD
computation. The NLO QCD+EW computation includes the LO contribution
$\mathcal{O}(\alpha_s\alpha)$ and the NLO contributions
$\mathcal{O}(\alpha_s^2\alpha)$ and $\mathcal{O}(\alpha_s\alpha^2)$.
We do not consider the LO PI contribution $\mathcal{O}(\alpha^2)$ and the
corresponding higher-order EW correction. EW corrections for this process
were computed in Refs.~\cite{Bernreuther:2010ny,Hollik:2011ps,Kuhn:2011ri,Bernreuther:2012sx,Pagani:2016caq,Czakon:2017wor,Czakon:2017lgo,Czakon:2017mmr,Czakon:2019bcq,Czakon:2019txp}. The process receives contributions from
6 (36) parton luminositites at NLO QCD (NLO QCD+EW), mainly from $gg$ fusion.
